\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{lato}
\usepackage{geometry}

\definecolor{heading}{HTML}{2A363B}
\definecolor{subheading}{HTML}{4A6572}
\definecolor{link}{HTML}{258EA6}

\input{glyphtounicode}
\input{custom-command.tex}

% -------------------- FONT OPTIONS --------------------
\usepackage{charter}

\addtolength{\topmargin}{-4.08003pt}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot[L]{\color{gray}Last Updated on \today}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\geometry{
    a4paper,
    left=1cm,
    right=1cm,
    top=1cm,
    bottom=1cm,
    headheight=14pt,
    footskip=5pt
}

\urlstyle{same}

\raggedbottom{}
\raggedright{}
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------

\begin{center}
	\textbf{\Huge\scshape{HO VAN TOAN}}\vspace{8pt} \\
	\textbf{(Middle .Net Fullstack Engineer)}\vspace{8pt} \\
	\small
	\faIcon{phone}
	\href{tel:0336516906}{\underline{0336516906}}$ $
	\faIcon{github}
	\href{https://github.com/hvantoan}{\underline{github.com/hvantoan}}$ $
	\faIcon{linkedin}
	\href{https://linkedin.com/in/hvantoan}{\underline{linkedin.com/in/hvantoan}}$ $
	\faIcon{envelope}
	\href{mailto:it.vantoan@gmail.com}{\underline{it.vantoan@gmail.com}}
\end{center}

\vspace{10pt}
% -------------------- SKILLS --------------------
\section{Skills}
\skillList{
	\skill{Programming Languages}{C\#, JavaScript, and TypeScript}
	\skill{Frameworks/Platforms}{.NET Core/MVC, Redis, RabbitMQ, React/Next, Tailwind CSS, MUI UI, Shadcn}
	\skill{Databases}{SQL Server, PostgreSQL}
	\skill{Tools and Processes}{Git, CI/CD principles, Docker}
}

% -------------------- PROJECTS --------------------
\section{Experiences}

% VietInfo
\mainList{}{

	\company{PHU MY TECHNOLOGY AND CHEMICAL INVESTMENT CO., LTD --- .Net Fullstack Engineer}{C\#, NextJs (Freelance (Sa, Su), 12 members)}{June 2022 --- Now}
	\mainList{}{
		\experienceHeader{FMS Projects}{}{
			\projectdesc{A management system including CRM and CMS with e-commerce, sales management, inventory, shipping, authorization, reporting, etc., for web and mobile platforms.}
			\techused{C\#, .Net Core, PostgreSQL, ReactTS, Redis, RabbitMQ, Docker}
			\responsibilities{
				\respitem{Develop a comprehensive management system including CRM and CMS for web and mobile platforms.}
				\respitem{Implement a KYC system using gRPC and design the Audit Worker module with Markdown and RabbitMQ.}
				\respitem{Build and optimize the Report module, including website and APIs, based on Business Analyst requirements.}
				\respitem{Maintain, troubleshoot, and enhance the website and APIs according to tester reports.}
				\respitem{Maintain and enhance the system, applying microservices architecture and Domain-Driven Design (DDD).}
			}
		}
	}

	\company{VIETINFO TECH CORP --- .Net Fullstack Engineer}{C\#, ReactJS}{June 2022 --- Now}
	% Chat Project
	\mainList{}{
		\experienceHeader{Internal Chat Project}{(4 members)}{
			\projectdesc{A web application that enables departments to communicate, manage, and assign tasks. It supports over 200 concurrent users and integrates with APIs of other company products.}
			\techused{C\#, .Net Core, SQL Server, ReactTS, Material UI, Tailwind CSS}
			\responsibilities{
				\respitem{Develop a web chat feature with responsive design, optimized for all devices.}
				\respitem{Analyze requirements from the Project Manager (PM) to build and integrate APIs from other company products.}
				\respitem{Ensure system stability to support over 200 users.}
			}
		}
	}

	% Document Management
	\mainList{}{
		\experienceHeader{Document Management Project}{(8 members)}{
			\projectdesc{A CMS website that provides robust features like version control, secure access management, and audit trails to streamline workflows for managing a wide array of documents—including digital signatures, invitations, administrative paperwork, and more—while ensuring compliance and data integrity.}
			\techused{C\#, .Net Core, SQL Server, ReactTs, Devextreme, Bootstrap}
			\responsibilities{
				\respitem{Maintain and enhance the CMS website to ensure optimal performance and functionality.}
				\respitem{Resolve issues related to document and user workflows for a seamless experience.}
				\respitem{Collaborate with the back-end team to develop new features based on client requirements.}
				\respitem{Discuss improvements with the team to optimize the platform’s functionality and strengthen its security features.}
				\respitem{Refactor code from ASP.NET Web Forms to ReactJS to modernize the CMS, improving performance and scalability.}
			}
		}
	}

	\newpage
	\company{TMA Solutions --- Backend Developer}{C\#, Flutter}{January 2022 --- June 2022}
	\mainList{}{
		\experienceHeader{Pronest}{(6 members)}{
			\projectdesc{Develop an IoT device management system enabling viewing, updating, and automation of IoT devices.}
			\techused{C\#, .Net Core, SQL Server, Flutter}
			\responsibilities{
				\respitem{Develop an intuitive user interface for monitoring and managing the status of IoT devices.}
				\respitem{Integrate APIs for data collection and remote device control.}
				\respitem{Build a mechanism for automatically updating and adjusting device configurations as required.}
				\respitem{Ensure the security and stability of the system through regular testing and maintenance.}
			}
		}
	}
}

% -------------------- EXPERIENCE --------------------

\section{Projects}

\mainList{}{
	\experienceHeader{SEO Tool}{}{

		\projectdesc{A tool that helps users manage and optimize their website's SEO performance.}
		\techused{C\#, .Net Core, SQL Server, Blazor}
		\responsibilities{
			\respitem{Build an SEO analysis tool using .NET Core and Blazor, integrating a Google Search crawler for keyword analysis.}
			\respitem{Develop a rank tracking system to monitor post positions and indexing status.}
			\respitem{Optimize performance using MemoryCache, reducing latency and providing instant keyword suggestions.}
			\respitem{Extend the Blazor-based CMS with SEO analytics and automated reporting workflows.}
		}
	}

	\experienceHeader{Minder}{}{
		\projectdesc{A sports coordination platform enabling users to organize matches, discover players/teams, and manage sports activities.}
		\techused{RESTful APIs, SignalR, .Net Core, UI/UX design}
		\responsibilities{
			\respitem{Develop a sports coordination platform with real-time features using SignalR and RESTful APIs.}
			\respitem{Implement user authentication (email, phone, Google OAuth) with secure token management.}
			\respitem{Build a match discovery system with geolocation filtering and dynamic join/leave functionality.}
			\respitem{Integrate Firebase Cloud Messaging for push notifications about matches, messages, and team invitations.}
		}
	}
}

\end{document}
