
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in} % Default was -.5in
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

\begin{document}

\begin{flushright}
  \color{gray}
  \item
  Last Updated on April 26th, 2024
\end{flushright}

\vspace{-5pt}

\begin{center}
    \textbf{\Huge \scshape HO VAN TOAN} \\ \vspace{8pt}
    \small 
    \faIcon{github}
    \href{https://github.com/mattyDoe}{\underline{github.com/hvantoan}} $  $
    \faIcon{linkedin}
    \href{https://linkedin.com/in/mattydoe}{\underline{linkedin.com/in/hvantoan}} $  $
    \faIcon{envelope}
    \href{mailto:it.vantoan@gmail.com}
    {\underline{it.vantoan@gmail.com}}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ho Chi Minh City University of Technology}{June 2019}
      {B.S. Software engineering}{Current GPA: 3.45/4.0}
  \resumeSubHeadingListEnd

\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    
     \textbf{Languages}{: C\#, JavaScript/TypeScript, HTML/CSS} \\
     \textbf{Tools}{: Git/GitHub, VS Code, IntelliJ GoLand/IDEA}\\
     \textbf{Frameworks}{: .Net Framework, .NET Core , React/Next} \\
     \textbf{Libraries}{: Entity Framework, React  }\\
     
    }}
 \end{itemize}

\section{Projects}
    \resumeSubHeadingListStart

        \resumeProjectHeading
        {\textbf{FMS Project} $|$ \footnotesize\emph{C\#, NextJs, APIs, Git, Unix Shell, VS Code (Freelance)}}{January 2022 - Now}
        \item Team size: 6 members
        \item{Main responsibilities:}
        \resumeItemListStart
            \resumeItem{Build RESTful APIs using .NET Core 5x/6x with Entity Framework
 Core.}
            \resumeItem{ Research and apply tuning solutions, optimize the system in terms of
 performance and load capacity.}
            \resumeItem{ Implement new features, maintain and fix bugs for the Flutter
 (Mobile) and Blazor WebAssembly (Web).}
            \resumeItem{Design, implement a system for async data for commercial business
 using Redis, RabbitMQ}
        \resumeItemListEnd
        \item {Technologies used: C\#, ASP.NET Core, .Net 5x/6x, PostgreSQL, Redis,
RabitMQ, OpenXML, ClosedXML.}
\item {Recognition and Gains:}
\resumeItemListStart
\resumeItem{Understand well how to implement and operate a project. Know how
to solve problems quickly and ﬂexibly.}
\resumeItem{Good teamwork and communication skills. Work eﬀectively with QA,
tester, and Front-end developers.}
\resumeItem{Have rich experience in Back-end development: C#, Web API, Redis, RabitMQ, PostgreSQL, OpenXML, ClosedXML.}
\resumeItem{Have experience in Front-end developer: JavaScrip, Reacjs, Material UI, Redux-toolkit...}
\resumeItem{Good knowledge of data structures and algorithms.}

\section{Experience}
  \resumeSubHeadingListStart

          \resumeProjectHeading
          {\textbf{Competitive Programming Club} $|$ \footnotesize\emph{Member}\vspace{8pt}}{Sept. 2023 -- Present}
          {\small{Involved in the club centered around Competitive Programming}}

          \resumeProjectHeading
          {\textbf{Apex Tutoring}\vspace{8pt} $|$ \footnotesize\emph{Tutor}}{2019 -- Present}
          \small{Routinely tutor K--12 students in math, coding, etc.}

          \resumeProjectHeading
          {\textbf{Luigi Team Charity} $|$ \footnotesize\emph{Volunteer, Manager}\vspace{8pt}}{2018 -- Present}
          {\small{Earned an award for philanthropic hours spent, still giving away 100 stocked backpacks a year}}

        \subsection{Hobbies}
          
          \resumeProjectHeading
          {\textbf{Playing the Drums}\vspace{8pt}}{2013 -- 2019}
          {\small{Played the drums in symphonic, jazz, and marching bands}}

          \resumeProjectHeading
          {\textbf{3\textsuperscript{rd} Place Time Keeping Challenge Championship \footnotesize{(Time Keeping Assocation)}}\vspace{8pt}}{Feb. 2022 -- May 2022}
          {\small{Won \$1500 nationally competing against high school students in counting seconds and minutes}}
          
    \resumeSubHeadingListEnd 

\end{document}