\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}


% -------------------- FONT OPTIONS --------------------
\usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

\include{custom-command}

% -------------------- HEADING--------------------
\begin{flushright}
	\vspace{-4pt}
	\color{gray}
	\item
	Last Updated on Martch 07th, 2024
\end{flushright}

\vspace{-5pt}

\begin{center}
	\textbf{\Huge\scshape{HO VAN TOAN}}\vspace{8pt} \\
	\small
	\faIcon{github}
	\href{https://github.com/hvantoan}{\underline{github.com/hvantoan}} $  $
	\faIcon{linkedin}
	\href{https://linkedin.com/in/hvantoan}{\underline{linkedin.com/in/hvantoan}} $  $
	\faIcon{envelope}
	\href{mailto:it.vantoan@gmail.com}
	{\underline{it.vantoan@gmail.com}}
\end{center}

% -------------------- SKILLS --------------------
\section{Skills}
\skillList{
	\skill{Programming Languages}{C\#, JavaScript \& TypeScript}
	\skill{Frameworks/Platforms}{.NET Core/MVC, ReactJs, NextJs, Redux, Tailwind CSS, MUI UI, Redis, RabbitMQ}
	\skill{Databases}{SQL Server, PostgreSQL}
	\skill{Tools \& Processes}{Git, CI/CD, Docker}
}

% -------------------- PROJECTS --------------------
\section{Experiences}


% VietInfo
\mainList{}{
	\company{CONG TY CO PHAN VIETINFO --- Fullstack developer}{C\#, ReactJS}{June 2022 --- Now}
	% Chat Project
	\mainList{}{
		\projectheader{Internal Chat Project}{(4 members)}{
			\projectdesc{A web application that enables departments to communicate, manage, and assign tasks. It supports over 200 concurrent users and integrates with APIs of other company products.}
			\techused{C\#, .Net Core, SQL Server, ReactTS, Material UI, Tailwind CSS}
			\responsibilities{
				\respitem{Develop a web chat feature with responsive design, optimized for all devices.}
				\respitem{Analyze requirements from the Project Manager (PM) to build and integrate APIs from other company products.}
				\respitem{Ensure system stability to support over 200 concurrent users.}
			}
		}

		% Quan ly van ban
		\projectheader{QLVB Project}{(8 members)}{
			\projectdesc{A CMS website that provides robust features like version control, secure access management, and audit trails to streamline workflows for managing a wide array of documents—including digital signatures, invitations, administrative paperwork, and more—while ensuring compliance and data integrity.}
			\techused{C\#, .Net Core, SQL Server, ReactTS, Devextreme, Bootstrap}
			\responsibilities{
				\respitem{Maintain and enhance the CMS website to ensure optimal performance and functionality.}
				\respitem{Resolve issues related to document and user workflows for a seamless experience.}
				\respitem{Collaborate with the back-end team to develop new features based on client requirements.}
				\respitem{Discuss improvements with the team to optimize the platform’s functionality and strengthen its security features.}
				\respitem{Refactor code from ASP.NET Web Forms to ReactJS to modernize the CMS, improving performance and scalability.}
			}
		}
	}

	\company{FMS --- Fullstack developer}{C\#, NextJs (Freelance)}{January 2022 --- Now}
	\mainList{}{
		\projectheader{FMS Project}{12 members}{
			\projectdesc{A management system including CRM and CMS with e-commerce, sales management, inventory, shipping, authorization, reporting,... for web and mobile platforms.}
			\techused{C\#, .Net Core, SQL Server, ReactTS, Redis, RabbitMQ, Docker}
			\responsibilities{
				\respitem{Develop a KYC system using gRPC.}
				\respitem{Build and design the Audit Worker module with Markdown and RabbitMQ.}
				\respitem{Develop and design the website and APIs for the Report module based on Business Analyst (BA) requirements.}
				\respitem{Maintain, troubleshoot, and enhance the website and APIs according to tester reports.}
				\respitem{Develop the module for managing receipts, payments, and debt records.}
				\respitem{Work with Domain-Driven Design (DDD) and microservices architecture.}
			}
		}
	}
}



% -------------------- EXPERIENCE --------------------
\section{Projects}

\mainList{}{
	\projectheader{SEO Tool}{}{
		\projectdesc{A tool that helps users manage and optimize their website's SEO performance.}
		\techused{C\#, .Net Core, SQL Server, Blazor}
		\responsibilities{
			\respitem{Developed a Google Search crawler to extract TOP 10/50/100 results for keyword analysis and SEO recommendations.}
			\respitem{Engineered a rank tracking system monitoring post positions, indexing status, and optimization strategies.}
			\respitem{Optimized performance using MemoryCache for instant keyword suggestions and reduced latency.}
			\respitem{Extended Blazor-based CMS with modules for SEO analytics and automated reporting workflows.}
			\respitem{Designed relational databases with EF Core and optimized queries using LINQ for large datasets.}
		}
	}
}

\mainList{}{
	\projectheader{Minder}{}{
		\projectdesc{A sports coordination platform enabling users to organize matches, discover players/teams, and manage sports activities.}
		\techused{RESTful APIs, SignalR, real-time databases, UI/UX design}
		\responsibilities{
			\respitem{Designed and implemented user authentication flows (email, phone, Google OAuth) with secure token management.}
			\respitem{Developed RESTful APIs for profile/team management, including avatar uploads, contact updates, and team roster controls.}
			\respitem{Built real-time features using WebSocket: in-app messaging for teams/opponents and live match updates.}
			\respitem{Created a match discovery system with geolocation filtering, time-based search, and dynamic join/leave functionality.}
			\respitem{Integrated Firebase Cloud Messaging for push notifications about matches, messages, and team invitations.}
			\respitem{Optimized UI/UX for team creation workflows, including member invitations and role-based access controls.}
		}
	}
}

\end{document}
