% ================================================================================
% EXPERIENCES SECTION
% ================================================================================
% Professional work experience

\section{Experiences}

\mainList{}{

    % --------------------------------------------------------------------------
    % PHU MY TECHNOLOGY
    % --------------------------------------------------------------------------
    \company{PHU MY TECHNOLOGY AND CHEMICAL INVESTMENT CO., LTD --- .Net Fullstack Engineer}{C\#, NextJs (Freelance (Sa, Su), 12 members)}{June 2022 --- Now}
    \mainList{}{
        \experienceHeader{FMS Projects}{}{
            \projectdesc{A management system including CRM and CMS with e-commerce, sales management, inventory, shipping, authorization, reporting, etc., for web and mobile platforms.}
            \techused{C\#, .Net Core, PostgreSQL, ReactTS, Redis, RabbitMQ, Docker}
            \responsibilities{
                \respitem{Develop a comprehensive management system including CRM and CMS for web and mobile platforms.}
                \respitem{Implement a KYC system using gRPC and design the Audit Worker module with Markdown and RabbitMQ.}
                \respitem{Build and optimize the Report module, including website and APIs, based on Business Analyst requirements.}
                \respitem{Maintain, troubleshoot, and enhance the website and APIs according to tester reports.}
                \respitem{Maintain and enhance the system, applying microservices architecture and Domain-Driven Design (DDD).}
            }
        }
    }

    % --------------------------------------------------------------------------
    % VIETINFO TECH CORP
    % --------------------------------------------------------------------------
    \company{VIETINFO TECH CORP --- .Net Fullstack Engineer}{C\#, ReactJS}{June 2022 --- Now}

    % Internal Chat Project
    \mainList{}{
        \experienceHeader{Internal Chat Project}{(4 members)}{
            \projectdesc{A web application that enables departments to communicate, manage, and assign tasks. It supports over 200 concurrent users and integrates with APIs of other company products.}
            \techused{C\#, .Net Core, SQL Server, ReactTS, Material UI, Tailwind CSS}
            \responsibilities{
                \respitem{Develop a web chat feature with responsive design, optimized for all devices.}
                \respitem{Analyze requirements from the Project Manager (PM) to build and integrate APIs from other company products.}
                \respitem{Ensure system stability to support over 200 users.}
            }
        }
    }

    % Document Management Project
    \mainList{}{
        \experienceHeader{Document Management Project}{(8 members)}{
            \projectdesc{A CMS website that provides robust features like version control, secure access management, and audit trails to streamline workflows for managing a wide array of documents—including digital signatures, invitations, administrative paperwork, and more—while ensuring compliance and data integrity.}
            \techused{C\#, .Net Core, SQL Server, ReactTs, Devextreme, Bootstrap}
            \responsibilities{
                \respitem{Maintain and enhance the CMS website to ensure optimal performance and functionality.}
                \respitem{Resolve issues related to document and user workflows for a seamless experience.}
                \respitem{Collaborate with the back-end team to develop new features based on client requirements.}
                \respitem{Discuss improvements with the team to optimize the platform's functionality and strengthen its security features.}
                \respitem{Refactor code from ASP.NET Web Forms to ReactJS to modernize the CMS, improving performance and scalability.}
            }
        }
    }

    \newpage

    % --------------------------------------------------------------------------
    % TMA SOLUTIONS
    % --------------------------------------------------------------------------
    \company{TMA Solutions --- Backend Developer}{C\#, Flutter}{January 2022 --- June 2022}
    \mainList{}{
        \experienceHeader{Pronest}{(6 members)}{
            \projectdesc{Develop an IoT device management system enabling viewing, updating, and automation of IoT devices.}
            \techused{C\#, .Net Core, SQL Server, Flutter}
            \responsibilities{
                \respitem{Develop an intuitive user interface for monitoring and managing the status of IoT devices.}
                \respitem{Integrate APIs for data collection and remote device control.}
                \respitem{Build a mechanism for automatically updating and adjusting device configurations as required.}
                \respitem{Ensure the security and stability of the system through regular testing and maintenance.}
            }
        }
    }
}
