% ================================================================================
% PROJECTS SECTION
% ================================================================================
% Personal and side projects

\section{Projects}

\mainList{}{

    % --------------------------------------------------------------------------
    % SEO TOOL
    % --------------------------------------------------------------------------
    \experienceHeader{SEO Tool}{}{
        \projectdesc{A tool that helps users manage and optimize their website's SEO performance.}
        \techused{C\#, .Net Core, SQL Server, Blazor}
        \responsibilities{
            \respitem{Build an SEO analysis tool using .NET Core and Blazor, integrating a Google Search crawler for keyword analysis.}
            \respitem{Develop a rank tracking system to monitor post positions and indexing status.}
            \respitem{Optimize performance using MemoryCache, reducing latency and providing instant keyword suggestions.}
            \respitem{Extend the Blazor-based CMS with SEO analytics and automated reporting workflows.}
        }
    }

    % --------------------------------------------------------------------------
    % MINDER
    % --------------------------------------------------------------------------
    \experienceHeader{Minder}{}{
        \projectdesc{A sports coordination platform enabling users to organize matches, discover players/teams, and manage sports activities.}
        \techused{RESTful APIs, SignalR, .Net Core, UI/UX design}
        \responsibilities{
            \respitem{Develop a sports coordination platform with real-time features using SignalR and RESTful APIs.}
            \respitem{Implement user authentication (email, phone, Google OAuth) with secure token management.}
            \respitem{Build a match discovery system with geolocation filtering and dynamic join/leave functionality.}
            \respitem{Integrate Firebase Cloud Messaging for push notifications about matches, messages, and team invitations.}
        }
    }
}
